---
title: "assignment_1"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
date: "2022-11-23"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(modelsummary)
library(ggplot2)
library(plotrix)
```

```{r load df, include=FALSE}
df <- read_csv('https://osf.io/4ay9x/download')
```

## We would like to look at the unconditional income difference bewteen men and female Lawyers, Judges, magistrates, and other judicial workers (occ2012 = 2100)
```{r echo=FALSE, message=FALSE, warning=FALSE}
df <- df %>% 
  filter(!is.na(hhid)) %>% 
  filter(occ2012 == 2100)

diff_mw <- df %>% 
  select(sex, earnwke) %>% 
  group_by(sex) %>% 
    summarise(mean_earning = mean(earnwke),
            numObs = n())
diff_mw <- diff_mw %>% add_row(sex = NA , mean_earning = diff(diff_mw$mean_earning), numObs = sum(diff_mw$numObs))
diff_mw
```
We can see that the difference in unconditional weekly gender pay gap between men and women is $298 on average in 1027 observations.  

## Gender pay gap with education difference
```{r echo=FALSE, message=FALSE, warning=FALSE}
edu_men <- df %>% group_by(grade92) %>% 
  filter(sex == 1) %>% 
  select(sex, earnwke) %>% 
  summarise(mean_earning_m = mean(earnwke))

edu_women <- df %>% group_by(grade92) %>% 
  filter(sex == 2) %>% 
  select(sex, earnwke) %>% 
  summarise(mean_earning_wm = mean(earnwke))

diff_edu <- merge(x=edu_men,y=edu_women,by.x="grade92",by.y = "grade92",all= T)

colors <- c("Men" = "navyblue", "Women" = "red")

diff_edu_plot <- ggplot(diff_edu, aes(x = diff_edu$grade92)) +
    geom_point(aes(y = mean_earning_m, color = "Men"), size = 2) +
    geom_smooth(aes(y = mean_earning_m, color = "Men"), method = 'lm', se = FALSE) +
    geom_point(aes(y = mean_earning_wm, color = "Women"), size = 2) +
    geom_smooth(aes(y = mean_earning_wm, color = "Women"), method = 'lm', se = FALSE) +
      labs(x= 'Education Level', y= 'Average weekly earnings', color = 'Legend')+
      scale_color_manual(values = colors) +
  theme_classic() + 
  theme(axis.line = element_line(arrow = arrow(type='closed', length = unit(10,'pt'))), axis.ticks.x=element_blank(), axis.text.x=element_blank())+
  xlim(37,47) +
  ggtitle('Difference of earnings between men and women lawyers', 'with different educational level')

diff_edu_plot
```

From the regression line, we can see that Men Lawyers have higher earnings than Women Lawyers on all the education levels, while the average earning of both genders tend to increase with higher education qualification.  
  
## Correlation Coefficient between educational level and average earnings of men and women lawyers
```{r echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
diff_edu$diff <- diff_edu$mean_earning_m - diff_edu$mean_earning_wm

diff_edu <- diff_edu %>% filter(!is.na(mean_earning_m)) %>% 
  filter(!is.na(mean_earning_wm))
```

Correlation Coefficient between educational level and average earnings of men lawyers
```{r message=FALSE, warning=FALSE}
cor(diff_edu$grade92, diff_edu$mean_earning_m)
```

Correlation Coefficient between educational level and average earnings of women lawyers
```{r message=FALSE, warning=FALSE}
cor(diff_edu$grade92, diff_edu$mean_earning_wm)
```

## Regression Coefficients
β0 and β1 of men lawyers earnings dependent on their education level
```{r message=FALSE, warning=FALSE}
lm(diff_edu$mean_earning_m ~ diff_edu$grade92)
```
Standard Error of sample with the regression value of men lawyers earnings dependent on their education level
```{r message=FALSE, warning=FALSE}
std.error(diff_edu$mean_earning_m)
```

β0 and β1 of women lawyers earnings dependent on their education level
```{r message=FALSE, warning=FALSE}
lm(diff_edu$mean_earning_wm ~ diff_edu$grade92)
```

Standard Error of sample with the regression value of women lawyers earnings dependent on their education level
```{r message=FALSE, warning=FALSE}
std.error(diff_edu$mean_earning_wm)
```

